Tracking Rodinia into the Neoproterozoic: new paleomagnetic constraints from the Jacobsville Formation

### 2024-01-23 Manuscript/support_info.tex
update manuscript for proof

\begin{document}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\subsection*{Supporting Information for ``Tracking Rodinia in the Neoproterozoic: new paleomagnetic constraint from the Jacobsville Formation"}
Yiming Zhang\textsuperscript{1}, Eben B. Hodgin\textsuperscript{1}, Tadesse Alemu\textsuperscript{1}, James Pierce\textsuperscript{1,2}, Anthony Fuentes\textsuperscript{1}, Nicholas L. Swanson-Hysell\textsuperscript{1}

@@

% $^{2}$Department of Earth, Environmental and Planetary Sciences, Brown University, RI, USA

$^{2}$Department of Earth and Planetary Sciences, Yale University, New Haven, CT, USA}

\listoffigures
\listoftables
\tableofcontents

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=0.9\textwidth]{SI_hct.pdf}
\caption{Jacobsville chemical remanence magnetization directions plotted by section. Samples collected from the Natural Wall section do not have interpretable chemical remanence component that can be fit with least-squares lines. }
\label{fig:Jacobsville_CRM}
\end{figure*}

@@

Haliburton Intrusions                                      & -32.6    & 141.9    & 6.3  & \cite{Warnock2000a}                          & 1015       & 1000     & 1030     & \cite{Warnock2000a}                                          \\

>>>>

\begin{document}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\subsection*{Supporting Information for ``Tracking Rodinia in the Neoproterozoic: new paleomagnetic constraint from the Jacobsville Formation"}
Yiming Zhang\textsuperscript{1}, Eben B. Hodgin\textsuperscript{1,2}, Tadesse Alemu\textsuperscript{1}, James Pierce\textsuperscript{1,3}, Anthony Fuentes\textsuperscript{1}, Nicholas L. Swanson-Hysell\textsuperscript{1}

@@

$^{2}$Department of Earth, Environmental and Planetary Sciences, Brown University, RI, USA

$^{3}$Department of Earth and Planetary Sciences, Yale University, New Haven, CT, USA}

\listoffigures
\listoftables
%\tableofcontents

\begin{figure*}[h!]
\centering
\includegraphics[width=0.9\textwidth]{Manuscript/SI_petrography.png}
\caption{Side-by-side reflected light and oblique illumination images of a thin section of the same field of view of sample NW2-7 collected from Natural Wall ravine. The white arrows point towards examples of large sub-milimeter-scale detrital hematite grains that have bright reflectance under reflected light. Almost all subangular grains in grey color in the reflected image are quartz grains. The red color in the oblique illumination image is a result of diffuse reflectance of pigmentary hematite grains that often coat the boundaries of detrital grains. }
\label{fig:SI_orthogonal}
\end{figure*}

\begin{figure*}[h!]
\centering
\includegraphics[width=0.5\textwidth]{Manuscript/SI_orthogonal.pdf}
\caption{Representative orthogonal vector diagrams of demagnetization experiments for specimens from different stratigraphic sections of this study. An overprint component subparallel to the present day field direction in the study area is typically minimally present in siltstone to very fine-grained sandstone facies. This component shown in light green can be fit with a least-squares line in fine-grained facies. After the removal of the low-temperature component, a mid-temperature component typically unblocks through a wide range of temperature steps by up to $\sim$650\textdegree C. Finally, an origin-trending component with typically a shallower inclination than that of the mid-temperature component sharply unblocks through heating with smaller temperature intervals up toward the N\'eel temperature of hematite ($\sim$690\textdegree C). AF-Agate Falls section; HF-Hungarian side falls section near Dover Creek; JK-Hammel Creek section; SC-Snake Creek tributary section. M-magnetic moment; NRM-natural remanent magnetic moment. All diagrams are shown in tilt-corrected coordinates.}
\label{fig:SI_orthogonal}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=0.9\textwidth]{SI_hct.pdf}
\caption{Jacobsville chemical remanence magnetization directions plotted by section. Samples collected from the Natural Wall section do not have interpretable chemical remanence component that can be fit with least-squares lines. All directions are plotted in geographic coordinates.}
\label{fig:Jacobsville_CRM}
\end{figure*}

\begin{figure*}[h!]
\centering
\includegraphics[width=0.75\textwidth]{Manuscript/SI_Jacobsville_vs_Appalachian_poles.pdf}
\caption{Jacobsville detrital remanence Kent mean pole position and chemical remanence Fisher mean pole position (in geographic coordinates) plotted in context of Laurentia's paleomagnetic poles during Appalachian orogeny (ca. 460-260 Ma) as compiled in \cite{Torsvik2012a}. The mean chemical remanence pole position from the Snake Creek tributary section is plotted in context of the ca. 970-960 Ma poles developed by \cite{Brown2012a} from the Adirondack Highlands of the Grenville orogen. That this chemical remanence component failed a fold test (Figure S4) and yields a pole position that overlaps with the Grenville poles are consistent with the interpretation that the chemical remanence of the Jacobsville Formation at this locality was acquired  during the early Neoproterozoic, soon after Jacobsville deposition and deformation. That the Jacobsville DRM and CRM mean poles are distinct and far away from any of Laurentia's mid- to late-Paleozoic poles supports the interpretation that the Jacobsville detrital remanence magnetization was acquired during the Rigolet phase of the Grenvillian orogeny and the chemical remanence overprint was likely acquired soon after deposition as discussed in detail in the manuscript.}
\label{fig:Jacobsville_Appalachian}
\end{figure*}

@@

Haliburton Intrusions                                      & -36.2    & 141.7    & 6.0  & \cite{Buchan1976a}                          & 1015       & 1000     & 1030     & \cite{Warnock2000a}                                          \\
